Observed vs. Simulated Year Comparison

### 2023-03-01 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd
Misc Rmd updates
* Add specification that content should be returned to console if ran interactively
* Updates any call of stringr::FUNC(..., pattern = "") to pattern = "."
* Corrected errors in MCMC diagnostics that were causing failure to run
Update egg-to-parr surv output plots
* Include a set of plots showing survival as a time series
* Include set of plots showing fitted beverton holt on the scale of egg-to-parr survival vs. egg abundance
* Discard old "parr per egg" plot set
* Discard parr per spawner plot set

## Beverton-Holt

All red components are posterior summaries (medians and 95% credible intervals). The black curve is from an `nls()` fit on reconstructed parr and roughly approximated total egg production -- the grey region is the confidence interval around this fit.

@@

## Parr per Egg

This figure shows the density dependence built in to the Beverton-Holt recruitment function: with increasing egg density, survival per egg decreases. The horizontal line/region shows the theoretical maximum ($\alpha_j$) in the absence of density dependence.

```{r parr-per-egg-v-eggs, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total egg production by brood year
  E = post_summ(post, sub_index("^E[year,pop]", pop = j, year = ts_yrs))

  # conversion rates
  Pb_per_E = post_summ(post, sub_index("^Pb_per_E[year,pop]", pop = j, year = ts_yrs))

  # max survival
  alpha = post_summ(post, sub_index("^alpha[pop]", pop = j))

  # empty plot
  plot(Pb_per_E["mean",] ~ E["mean",],
       ylim = c(0, 1),
       xlim = c(0, max(E["97.5%",])), type = "n",
       ylab = "", xlab = "", las = 1, xaxt = "n", main = pops[j])

  # x-axis
  x_ticks = axisTicks(par("usr")[1:2], log = F)
  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)

  segments(E["2.5%",], Pb_per_E["mean",], E["97.5%",], Pb_per_E["mean",], col = alpha("red", 0.5))
  segments(E["mean",], Pb_per_E["2.5%",], E["mean",], Pb_per_E["97.5%",], col = alpha("red", 0.5))
  points(Pb_per_E["mean",] ~ E["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)

  rect(par("usr")[1], alpha["2.5%",], par("usr")[2], alpha["97.5%",], border = alpha("red", 0.5), col = alpha("salmon", 0.5))
  abline(h = alpha["mean",], lwd = 2, col = "red")
  box()
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
mtext(side = 2, outer = T, line = 0.25, "Parr per Egg")
```

## Parr per Spawner

This figure is identical to above, but shows parr production per spawner instead of per egg.

```{r parr-per-spawner-v-spawners, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior summaries of total spawners by brood year
  Sa_tot = post_summ(post, sub_index("^Sa_tot[year,pop]", pop = j, year = ts_yrs))

  # conversion rates
  Pb_per_Sa_tot = post_summ(post, sub_index("^Pb_per_Sa_tot[year,pop]", pop = j, year = ts_yrs))

  # empty plot
  plot(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",],
       ylim = c(0, max(Pb_per_Sa_tot["97.5%",])),
       xlim = c(0, max(Sa_tot["97.5%",])), type = "n",
       ylab = "", xlab = "", las = 1)

  segments(Sa_tot["2.5%",], Pb_per_Sa_tot["mean",], Sa_tot["97.5%",], Pb_per_Sa_tot["mean",], col = alpha("red", 0.5))
  segments(Sa_tot["mean",], Pb_per_Sa_tot["2.5%",], Sa_tot["mean",], Pb_per_Sa_tot["97.5%",], col = alpha("red", 0.5))
  points(Pb_per_Sa_tot["mean",] ~ Sa_tot["mean",], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Total Spawners")
mtext(side = 2, outer = T, line = 0.25, "Parr per Spawner")
```

>>>>

## Survival Time Series

```{r phi_E_Pb-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
               yrs = all_yrs[ts_yrs],
               main = pops[j])
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Egg-to-Parr Survival")
```

## Survival vs. Total Egg Production

This is the scale the Beverton-Holt recruitment function is estimated on.

```{r egg-surv-vs-eggs, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  # extract posterior samples of the BH productivity and capacity parameters
  alpha = post_subset(post, sub_index("alpha[pop]", pop = j), matrix = TRUE)
  beta = post_subset(post, sub_index("beta[pop]", pop = j), matrix = TRUE)

  # extract posterior summaries egg-to-parr survival by brood year
  phi_E_Pb = post_summ(post, sub_index("^phi_E_Pb[year,pop]", pop = j, year = ts_yrs))

  # predict egg-to-parr survival along a sequence of egg abundances
  E_pred = seq(0, max(E[5,]), length = 30)
  phi_E_Pb_pred = t(sapply(1:post_dim(post, "saved"), function(i) 1/(1/alpha[i,] + E_pred/beta[i,])))
  colnames(phi_E_Pb_pred) = paste0("phi_E_Pb_pred[", 1:length(E_pred), "]")
  phi_E_Pb_pred = post_convert(cbind(postpack:::id_mat(post), phi_E_Pb_pred))
  phi_E_Pb_pred = post_summ(phi_E_Pb_pred, "Pb_pred")

  # empty plot
  plot(1, 1, type = "n", xlim = range(0, E[5,]), ylim = range(0, phi_E_Pb[5,], phi_E_Pb_pred[5,]),
       xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = pops[j])

  x_ticks = axisTicks(par("usr")[1:2], log = FALSE)
  y_ticks = axisTicks(par("usr")[3:4], log = FALSE)
  axis(side = 1, at = x_ticks, labels = x_ticks/1e6)
  axis(side = 2, at = y_ticks)

  # draw fitted relationship
  polygon(c(E_pred, rev(E_pred)), c(phi_E_Pb_pred[4,], rev(phi_E_Pb_pred[5,])), col = alpha("salmon", 0.5), border = NA)
  lines(phi_E_Pb_pred[4,] ~ E_pred, col = "red", lty = 2)
  lines(phi_E_Pb_pred[5,] ~ E_pred, col = "red", lty = 2)
  lines(phi_E_Pb_pred[3,] ~ E_pred, col = "red", lwd = 2)

  # draw state pairs + uncertainty
  segments(E[4,], phi_E_Pb[3,], E[5,], phi_E_Pb[3,], col = alpha("red", 0.5))
  segments(E[3,], phi_E_Pb[4,], E[3,], phi_E_Pb[5,], col = alpha("red", 0.5))
  points(phi_E_Pb[3,] ~ E[3,], pch = 21, col = "red", bg = alpha("salmon", 0.5), cex = 1.2)
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Total Egg Production (Millions)")
mtext(side = 2, outer = T, line = 0.25, "Egg-to-Parr Survival")
```

## Parr vs. Total Egg Production

Parr abundance is the product of egg-to-parr survival and total egg production; in this way we can back-out the standard Beverton-Holt function.

@@
